SIG Proceedings Paper in LaTeX Format

### 2019-08-30 SAC/submission/ACM_SigConf_SAC2020-2020_1.0/includes/discussion.tex
final changes draft paper

\subsubsection{Shuffling and learning rate with SGD}
In this subsubsection we will use the term SGD for SGD, Momentum and NAG, and advanced optimzers for Adagrad and Adam. The models was able to use a higher learning rates when SGD optimizers where combined with input shuffling in comparison to as when not, as shown in Figures \ref{fig:results_sgd}, \ref{fig:results_mom} and \ref{fig:results_nag}. Therefore, arises the questions why these phenomena happen, especially as it did not happen with advanced optimizers.  \\
First, we suspect our batched version of the Skip-Gram model with negative sampling (SGNS), to be at the origin of this phenomena. In consequence to this batched version, when input shuffling is not used a lot of words will appear multiple times in the same batch, as explained in Section \ref{ssec:shuffling}. Therefore, the gradients will be an average of all the training samples. When the input is shuffled, less words will appear multiple time which will make the gradients more precise.\\
Second, advanced optimizers have a way to counter-attack this issue, namely adaptive learning rates, explained in Section \ref{ssec:results_adagrad}. Adaptive learning rates counter attack the issue in the following way: high frequency words  will appear more often multiple times in a batch, they will also have lower learning rates. Therefore the impact of appearing in the same batch will be reduced. \\  The two above arguments could explain why a higher learning rate combined with SGD achieved better results with input shuffling but not when advanced optimizers are used.

\iffalse
\subsubsection{Large differences with NAG and SGD when using shuffling}
SGD and NAG both have very different values when using shuffling in comparison to unshuffled input, as shown in figures \ref{fig:results_sgd} and \ref{fig:results_nag}. We do not only attribute those results to input shuffling but partially also to a good random initialization guess. Due to a lack of time these experiments were not replicate more than once.
\fi

>>>>

\subsubsection{Shuffling and learning rate with SGD}
In this subsubsection we will use the term SGD for SGD, Momentum and NAG, and advanced optimzers for Adagrad and Adam. The models was able to use a higher learning rates when SGD optimizers where combined with input shuffling in comparison to as when not, as shown in Figures \ref{fig:results_sgd}, \ref{fig:results_mom} and \ref{fig:results_nag}. Therefore, arises the questions why these phenomena happen, especially as it did not happen with advanced optimizers.  \\
First, we suspect our batched version of the Skip-Gram model with negative sampling (SGNS), to be at the origin of this phenomena. In consequence to this batched version, when input shuffling is not used a lot of words will appear multiple times in the same batch, as explained in Section \ref{ssec:shuffling}. Therefore, the gradients will be an average of all the training samples. When the input is shuffled, less words will appear multiple time which will make the gradients more precise.\\
Second, advanced optimizers have a way to counter-attack this issue, namely adaptive learning rates. Adaptive learning rates counter attack the issue in the following way: high frequency words  will appear more often multiple times in a batch, they will also have lower learning rates. Therefore the impact of appearing in the same batch will be reduced. \\  The two above arguments could explain why a higher learning rate combined with SGD achieved better results with input shuffling but not when advanced optimizers are used.

\iffalse
\subsubsection{Large differences with SGD when using shuffling}
SGD and NAG both have very different values when using shuffling in comparison to unshuffled input, as shown in figures \ref{fig:results_sgd} and \ref{fig:results_nag}. We do not only attribute those results to input shuffling but partially also to a good random initialization guess. Due to a lack of time these experiments were not replicate more than once.
\fi

### 2019-08-30 SAC/submission/ACM_SigConf_SAC2020-2020_1.0/includes/results.tex
final changes draft paper

\subsection{Advanced Batches Version}
The advanced batched version is largely dependent on the definition of outlier. As shown in Table if the value for outliers is too small then the model convergence into score that is too small. If the threshold is higher training time is increased. We found that 99\% is a good reference value. With this setting our model converged in 1 epoch for the text8 dataset, which is our best result, and 7 for the enwik9 corpus. A recap of all our results with the text8 dataset can be found in Table.

>>>>

\subsection{Advanced Batches Version}
The advanced batched version in combination with the deletion of outliers and Adam as it's optimizer greatly outperformed the other versions. With this setting our model converged in 1 epoch for the text8 dataset, which is our best result. A recap of all our results with the text8 dataset can be found in Table \ref{table:results_text8}.
